### 2018-02-13 paper/intro.tex
removed some typos

It's common nowadays to use a third party, i.e.\ someone else's computer (better 
known as the Cloud), as an intermediate to share files.
For instance, it's common for Alice to upload the file to e.g.\ Box, Dropbox or 
OneDrive and share the link with Bob who can then download it.
The goal of this work is to design a decentralized, distributed system where 
Alice can share files \emph{efforlessly} between her own devices, e.g.\ laptop, 
smartphone and tablet.
But Alice should also be able to use her smartphone to share a file on her home 
computer with Bob.
Since these are Alice's private devices, privacy is essential.
E.g.\ it would be devastating for Alice's privacy if Bob could stalk her by 
tracking her devices or discern usage patterns.

@@

We use a purely \ac{P2P} design.
We first provide \iac{P2P} design connecting Alice's own devices.
This decreases the risk of third-party behaviour tracking.
Then we also use \iac{P2P} design to connect Alice's and Bob's devices.
This requires some more care, in this case Bob can track Alice since his devices 
are interacting directly with hers.

>>>>

It is common nowadays to use a third party, i.e.\ someone else's computer (better 
known as the Cloud), as an intermediate to share files.
For instance, it is common for Alice to upload a file to e.g.\ Box, Dropbox or 
OneDrive and share the link with Bob who can then download it.
The goal of this work is to design a decentralized, distributed system where 
Alice can share files \emph{effortlessly} between her own devices, e.g.\ laptop, 
smartphone and tablet.
But Alice should also be able to use her smartphone to share a file on her home 
computer with Bob.
Since these are Alice's private devices, privacy is essential.
E.g.\ it would be devastating for Alice's privacy if Bob could stalk her by 
tracking her devices or discern usage patterns.

@@

We use a purely \ac{P2P} design.
We first provide \iac{P2P} design connecting Alice's own devices.
This decreases the risk of third-party behavior tracking.
Then we also use \iac{P2P} design to connect Alice's and Bob's devices.
This requires some more care, in this case Bob can track Alice since his devices 
are interacting directly with hers.
